negativeBinomial

### 2015-09-04 lengthModel/lengthModel.Rmd
updated length model

```{r}
library(Gmisc)
tableData <- cbind(summary(s)$statistics[1:(e[[i]])[2] + 1), 1], summary(s)$quantiles[1:(e[[i]])[2] + 1), c(1, 5)])
htmlTable(x=round(tableData, digits=2),
          caption=paste("Regression parameter estimates and CI's"),
          header = c("Estimate", "Lower 95% CI", "Upper 95% CI"),
          rowlabel = "Variables",
          rnames = c("Intercept",
                    "Net Size",
                    "August",
                    "September",
                    "Juvenile",
                    "Male",
                    "Unknown",
                    "standard deviation"))
```

>>>>

```{r}
library(Gmisc)
tableData <- cbind(summary(s)$statistics[1:(dim(e[[1]])[2] + 1), 1],
                   summary(s)$quantiles[1:(dim(e[[1]])[2] + 1), c(1, 5)])
htmlTable(x=round(tableData, digits=2),
          caption=paste("Regression parameter estimates and CI's"),
          header = c("Estimate", "Lower 95% CI", "Upper 95% CI"),
          rowlabel = "Variables",
          rnames = c("Intercept",
                    "Net Size",
                    "August",
                    "September",
                    "Juvenile",
                    "Male",
                    "Unknown",
                    "standard deviation"))
```
